The pollination trade-off

### 2019-03-12 paper/manuscript.Rmd
Edits to third section of the results

Of the four variables we considered, we found that a plant's mean visit effectiveness and abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a). 
Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (\@ref(S-tab:table-aic-fixed-models)).

@@

We used a PCA of the analysed species to investigate whether plants strategies are similar across communities or whether they are flexible, and therefore able to adapt to the community context. 
The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
The first component was dominated by changes in the visit effectiveness and the relative abundance, while the second component was dominated by the number of shared pollinators and the plant's functional originality. 
When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the strategies of a species do not seem to be close to each other. 
Indeed, when we measured the median distance between the plants coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` analysed species (Figure \@ref(fig:fig-pca)c).

>>>>

Of the four variables we considered, we found that a plant's mean visit effectiveness and abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a). 
Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values (Table \@ref(S-tab:table-aic-fixed-models)).

@@

We used a PCA of the analysed species to investigate whether plant's niche of competition for pollination are similar across communities or whether they are flexible, and therefore a reflection of the community context. 
The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
The first component was dominated by changes in visit effectiveness and relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality. 
When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the niches of any given species do not tend to be close to each other. 
Indeed, when we measured the median distance between the plants coordinates, we found that it was only significantly smaller than that of randomisations for only `r numbers2words(sum(median_distances < 0.05))` of the `r numbers2words(length(median_distances))` analysed species (Figure \@ref(fig:fig-pca)c).
